Dynamic Witnesses for Static Type Errors

### 2015-11-20 paper/pldi16-submission/interactive.tex
misc edits

\paragraph{Visualization Context}
%
The \emph{visualization context} of each expression $e$
in the visualization state \vstate is the (unique) linear chain
in which it the expression $e$ belongs.
%
We write $\vroot{\vstate}{e}$ for the \emph{first} (or root)
expression appearing in the visualization context of $e$ in
\vstate.

\paragraph{Commands}
Our debugger supports the following \emph{commands}, each of which
is parameterized by a single expression (vertex) selected from the
(current) visualization state:
%
\begin{itemize}
%
\item \stepforwardsym, \stepbackwardsym:
      show result of a single step forward or backward respectively,
%
\item \jumpforwardsym:
      show result of taking multiple steps (a \emph{``big''} step)
      upto the first beta-reduction forward or backward respectively,
%
\item \stepintosym:
      show result of stepping into a function call in a sub-term,
      isolating it from the context,

\item \stepoversym:
      show result of skipping over a function call in a sub-term.
\end{itemize}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.8\linewidth]{fac-steps.png}
\caption{A sequence of interactions with the trace of
  \texttt{fac 1}. The stuck term is red, in each node the redex is
  highlighted. Thick arrows denote a multi-step transition, thin arrows
  denote a single-step transition. We start in step 1. In step 2 we jump
  forward from the witness to the next function call. In step 3 we step
  into the recursive \texttt{fac 0} call, which spawns a new ``thread''
  of execution. In step 4 we take a single step forward from
  \texttt{fac 0}.}
\label{fig:nanomaly-factorial}
\end{figure}

>>>>

\paragraph{Visualization Context}
%
The \emph{visualization context} of each expression $e$
in the visualization state $\vstate$ is the (unique) linear chain
in which the expression $e$ belongs.
%
We write $\vroot{\vstate}{e}$ for the \emph{first} (or root)
expression appearing in the visualization context of $e$ in
$\vstate$.

\paragraph{Commands}
Our debugger supports the following \emph{commands}, each of which
is parameterized by a single expression (vertex) selected from the
(current) visualization state:
%
\begin{itemize}
%
\item \stepforwardsym, \stepbackwardsym:
      show the result of a single step forward or backward respectively,
%
\item \jumpforwardsym, \jumpbackwardsym:
      show the result of taking multiple steps (a \emph{``big''} step)
      upto the first beta-reduction forward or backward respectively,
%
\item \stepintosym:
      show the result of stepping into a function call in a sub-term,
      isolating it from the context,

\item \stepoversym:
      show the result of skipping over a function call in a sub-term.
\end{itemize}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{fac-steps.png}
\caption{A sequence of interactions with the trace of
  \texttt{fac 1}. The stuck term is red, in each node the redex is
  highlighted. Thick arrows denote a multi-step transition, thin arrows
  denote a single-step transition. We start in step 1. In step 2 we jump
  forward from the witness to the next function call. In step 3 we step
  into the recursive \texttt{fac 0} call, which spawns a new ``thread''
  of execution. In step 4 we take a single step forward from
  \texttt{fac 0}.}
\label{fig:nanomaly-factorial}
\end{figure}
